---
title: "Land Bank Stewardship Analyses"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# initialize and import

```{r}
# import libraries
library(tidyverse)
library(tidycensus)
library(sf)
library(readxl)
library(lubridate)
library(arcgisbinding)
library(haven)
library(reticulate)
library(mgcv)
library(lmerTest)
library(table1)
library(sjPlot)
library(stargazer)
library(gamm4)
library(magrittr)
library(spdep)
library(ncf)

# import data files
# kernel density data
stseg_kd_data <- read_csv("U:/HBHE/PhD/Bushman/Papers-Presentations/2020-HBHE Colloquium/Data/yvpc-stseg-injury-p1crime-dv-kernel-densities.csv")
parcel_kd_data <- read_csv("U:/HBHE/PhD/Bushman/Papers-Presentations/2020-HBHE Colloquium/Data/yvpc-parcel-injury-p1crime-dv-kernel-densities.csv")

# import flint shapefile
flint <- read_sf("U:/HBHE/PRC/GIS/Projects/MI-YVPC 2015-2020/Base Data/2018/Flint_MI_2018.gdb", "FL10_CityBoundary_v1") %>%
  st_transform(crs = 6498)

# create version with 1000m buffer
flint_1000m <- st_buffer(flint, 1000)

# flint parcels
flint_parcel <- read_sf("U:/HBHE/PRC/GIS/Projects/MI-YVPC 2015-2020/Base Data/2018/Flint_MI_2018.gdb", "FL18_MIYVPC_Parcels_v12") %>%
  st_transform(crs = 6498)


# flint parcel metadata
flint_parcel_md <- read_csv("U:/Secure/PRC/Data Repository/YVPC 2015-2020/_data-analysis/mow-cng-activity-parcel-counting-15-18.csv")
```

# Organize Flint Parcel Data

```{r}
# format the flint_parcel dataframe
flint_parcel <- rename_with(flint_parcel, tolower, -Shape) %>%
  dplyr::select(-shape_length, -shape_area) %>%
  mutate(block_group_id = str_c("26049", census_tract_2010, census_block_group_2010)) %>%
  select(miyvpc_parcel_id, parcel_id, block_group_id)

# calculate flint parcel centroids
flint_parcel_centroids <- st_centroid(flint_parcel)
flint_parcel_centroids <- cbind(flint_parcel_centroids, st_coordinates(flint_parcel_centroids))

# replace NAs in density variables with 0s
parcel_kd_data <- parcel_kd_data %>%
  mutate(across(matches("density_sqmile"), ~replace_na(., 0)))

# join parcel metadata to parcel KDE data
parcel_crime <- left_join(parcel_kd_data, flint_parcel_md, by = c("miyvpc_parcel_id" = "MIYVPC_Parcel_ID", "year"))

# join parcel_crime data to MIYVPC parcel data
parcel_crime <- left_join(parcel_crime, flint_parcel_centroids, by = c("miyvpc_parcel_id"))
```

# pull in census data

```{r}
# pull in census data from geodatabase
gc_bgs <- st_read("C:/Users/grego/Documents/ArcGIS/Projects/PRC Work/YVPC/yvpc-assault-injury-densities/yvpc-assault-injury-densities.gdb", "acs_2019") %>%
  select(GEOID, tot_pop, pop_dens, bg_area, disadvantage_index, sr_disadvantage_index)

# merge with parcel_crime data
parcel_crime <- left_join(parcel_crime, gc_bgs, by = c("block_group_id" = "GEOID"))
```

# set up dataframe for analysis

```{r}
# create parcel_crime data for analyses
parcel_crime <- parcel_crime %>%
  as.data.frame() %>%
  select(-Shape.x, -Shape.y) %>%
  mutate(any_reg_mow = ifelse(!is.na(n_mows) & n_mows > 2, 1, 0)) %>%
  mutate(
    year0 = year - 2015,
    year_cat = factor(year),
    any_reg_mow = ifelse(!is.na(n_mows) & n_mows > 2, 1, 0),
    any_maintenance = rowSums(select(., green_activity, board_activity, any_reg_mow, lease_lot), na.rm = T),
    any_maintenance = ifelse(any_maintenance > 0, T, F),
    ownmain = case_when(
      any_maintenance == TRUE ~ "maintained",
      any_maintenance == FALSE & lb_owned == 1 ~ "owned",
      any_maintenance == FALSE & lb_owned == 0 ~ "control",
      TRUE ~ NA_character_
    ),
    disadvantage_index = disadvantage_index,
    pop_dens = pop_dens * 1e6,
    gclb_property = factor(lb_owned),
    cng_area = factor(in_cng_area)
  ) %>%
  filter(year < 2019) %>%
  distinct()
```

# Calculate Nearest Maintained Parcel

```{r}
# 2015
int_parcels_15 <- parcel_crime %>%
  filter(
    any_maintenance == T,
    year == 2015
  ) %>%
  distinct() %>%
  st_as_sf(coords = c("X", "Y"), crs = 6498)

all_parcels_15 <- parcel_crime %>%
  filter(year == 2015) %>%
  distinct() %>%
  st_as_sf(coords = c("X", "Y"), crs = 6498)

nearest_int_15 <- st_nearest_feature(all_parcels_15, int_parcels_15)
parcel_dists_15 <- st_distance(all_parcels_15, int_parcels_15)

parcel_distances_15 <- all_parcels_15 %>%
  select(miyvpc_parcel_id) %>%
  mutate(
    index = 1:nrow(.),
    year = 2015,
    nearest_int = nearest_int_15
  )

parcel_distances_15$distances <- with(parcel_distances_15, parcel_dists_15[cbind(index, nearest_int_15)])

rm(parcel_dists_15)


# 2016
int_parcels_16 <- parcel_crime %>%
  filter(
    any_maintenance == T,
    year == 2016
  ) %>%
  distinct() %>%
  st_as_sf(coords = c("X", "Y"), crs = 6498)

all_parcels_16 <- parcel_crime %>%
  filter(year == 2016) %>%
  distinct() %>%
  st_as_sf(coords = c("X", "Y"), crs = 6498)

nearest_int_16 <- st_nearest_feature(all_parcels_16, int_parcels_16)
parcel_dists_16 <- st_distance(all_parcels_16, int_parcels_16)

parcel_distances_16 <- all_parcels_16 %>%
  select(miyvpc_parcel_id) %>%
  mutate(
    index = 1:nrow(.),
    year = 2016,
    nearest_int = nearest_int_16
  )

parcel_distances_16$distances <- with(parcel_distances_16, parcel_dists_16[cbind(index, nearest_int_16)])

rm(parcel_dists_16)


# 2017
int_parcels_17 <- parcel_crime %>%
  filter(
    any_maintenance == T,
    year == 2017
  ) %>%
  distinct() %>%
  st_as_sf(coords = c("X", "Y"), crs = 6498)

all_parcels_17 <- parcel_crime %>%
  filter(year == 2017) %>%
  distinct() %>%
  st_as_sf(coords = c("X", "Y"), crs = 6498)

nearest_int_17 <- st_nearest_feature(all_parcels_17, int_parcels_17)
parcel_dists_17 <- st_distance(all_parcels_17, int_parcels_17)

parcel_distances_17 <- all_parcels_17 %>%
  select(miyvpc_parcel_id) %>%
  mutate(
    index = 1:nrow(.),
    year = 2017,
    nearest_int = nearest_int_17
  )

parcel_distances_17$distances <- with(parcel_distances_17, parcel_dists_17[cbind(index, nearest_int_17)])

rm(parcel_dists_17)


# 2018
int_parcels_18 <- parcel_crime %>%
  filter(
    any_maintenance == T,
    year == 2018
  ) %>%
  distinct() %>%
  st_as_sf(coords = c("X", "Y"), crs = 6498)

all_parcels_18 <- parcel_crime %>%
  filter(year == 2018) %>%
  distinct() %>%
  st_as_sf(coords = c("X", "Y"), crs = 6498)

nearest_int_18 <- st_nearest_feature(all_parcels_18, int_parcels_18)
parcel_dists_18 <- st_distance(all_parcels_18, int_parcels_18)

parcel_distances_18 <- all_parcels_18 %>%
  select(miyvpc_parcel_id) %>%
  mutate(
    index = 1:nrow(.),
    year = 2018,
    nearest_int = nearest_int_18
  )

parcel_distances_18$distances <- with(parcel_distances_18, parcel_dists_18[cbind(index, nearest_int_18)])

rm(parcel_dists_18)


# combine everything
parcel_distances <- bind_rows(parcel_distances_15, parcel_distances_16, parcel_distances_17, parcel_distances_18) %>%
  as.data.frame() %>%
  select(miyvpc_parcel_id, year, dist_to_maintained = distances)

# merge to parcel_crime
parcel_crime <- left_join(parcel_crime, parcel_distances, by = c("miyvpc_parcel_id", "year"))
```

# Define vacant parcel subset to analyze

```{r}
# determine which parcels are in all waves, and don't change lb-class owner
keep_parcels <- parcel_crime %>%
  group_by(miyvpc_parcel_id) %>%
  summarise(
    n = n(),
    lb_owned = sum(lb_owned),
    vacant = sum(vacant)
  ) %>%
  filter(
    n == 4,
    lb_owned %in% c(0, 4),
    vacant == 4
  ) %>%
  ungroup() %$%
  miyvpc_parcel_id

# create vacant parcel subset
# filter out parcels that are "out-of-bounds"
vacantparcel_crime <- parcel_crime %>% 
  filter(
    miyvpc_parcel_id %in% keep_parcels,
    X < 4059597,
    block_group_id != "260499800001"
  )

# recode parcel condition in 2015 for parcels that were leased 3 years (2016-2018)
leased_parcels <- vacantparcel_crime %>%
  group_by(miyvpc_parcel_id) %>%
  summarize(years_leased = sum(lease_lot, na.rm = T)) %>%
  filter(years_leased == 3) %$%
  miyvpc_parcel_id %>%
  unique()
  
vacantparcel_crime <- vacantparcel_crime %>%
  mutate(
    ownmain = ifelse(miyvpc_parcel_id %in% leased_parcels, "maintained", ownmain),
    ownmain = factor(ownmain, levels = c("control", "maintained", "owned"))
  )

# exclude parcels that weren't owned by the land bank, but got more than 3 mows
mow_mistakes <- vacantparcel_crime %>%
  filter(lb_owned == FALSE, any_reg_mow == 1) %$%
  miyvpc_parcel_id %>%
  unique()

vacantparcel_crime <- vacantparcel_crime %>%
  filter(
    !miyvpc_parcel_id %in% mow_mistakes,
    miyvpc_parcel_id != "{AE52F0CA-F991-4542-A899-661C950BE26E}" 
  )
```

### Shortcut to vacantparcel_crime data ###

```{r}
# write vacant parcel subset to memory
# write_csv(vacantparcel_crime, "U:/HBHE/PhD/Bushman/Papers-Presentations/2021-Land Banks and Violence Prevention/Data/vacantparcel-crime-20210823.csv")

vacantparcel_crime <- read_csv("U:/HBHE/PhD/Bushman/Papers-Presentations/2021-Land Banks and Violence Prevention/Data/vacantparcel-crime-20210823.csv") %>%
  mutate(
    ownmain = factor(ownmain, levels = c("control", "maintained", "owned")),
    year_cat = factor(year_cat)
  )
```

# calculate spatial lag covariate measures

```{r}
# deduplicate street segments
# make the dataframe a spatial object
# project data using EPSG:6498, Michigan South (meters)
df_sf <- vacantparcel_crime %>%
  select(miyvpc_parcel_id, X, Y, ownmain) %>%
  distinct() %>%
  st_as_sf(coords = c("X", "Y"), crs = 6498)

df_sf_coords <- coordinates(as(df_sf, "Spatial"))

# calculate the inverse distance weights matrix (neighbors are parcels within 1000 meters)
# max(unlist(nbdists(knn2nb(knearneigh(df_sf_coords, k=1)), df_sf_coords)))
parcel_neighbors <- dnearneigh(df_sf_coords, 0, 1000)
parcel_neigh_dists <- nbdists(parcel_neighbors, df_sf_coords)
parcel_idw <- lapply(parcel_neigh_dists, function(x) (1/(x)))
parcel_weights <- nb2listw(parcel_neighbors, glist = parcel_idw, style = "B")
# parcel_weights <- nb2listw(parcel_neighbors) # turn off if IDW

# # calculate k nearest neighbors weights matrix (neighbors are 5 closest parcels)
# parcel_neighbors <- knearneigh(df_sf_coords, k = 10)
# parcel_weights <- nb2listw(knn2nb(parcel_neighbors))

# create reduced dataframe for calculating lagged variable
# project the coordinate data
parcel_lag <- vacantparcel_crime %>%
  select(miyvpc_parcel_id, X, Y, year, contains("summerdensity_sqmile")) %>%
  st_as_sf(coords = c("X", "Y"), crs = 6498)

# split data by time point
parcel_lag_list <- split(parcel_lag, parcel_lag$year)

# calculate lagged variables within each time point
parcel_lag_list <- lapply(parcel_lag_list, function(x){
  x$p1crime_summerdensity_lag             <- lag.listw(parcel_weights, x$p1crime_summerdensity_sqmile, zero.policy = FALSE)
  x$p1violcrime_summerdensity_lag         <- lag.listw(parcel_weights, x$p1violcrime_summerdensity_sqmile, zero.policy = FALSE)
  x$p1youthviolcrime_summerdensity_lag    <- lag.listw(parcel_weights, x$p1youthviolcrime_summerdensity_sqmile, zero.policy = FALSE)
  x$p1violguncrime_summerdensity_lag      <- lag.listw(parcel_weights, x$p1violguncrime_summerdensity_sqmile, zero.policy = FALSE)
  x$p1youthviolguncrime_summerdensity_lag <- lag.listw(parcel_weights, x$p1youthviolguncrime_summerdensity_sqmile, zero.policy = FALSE)
  return(x)
})

# combine all time points of lagged variable
parcel_lag <- do.call("bind_rows", parcel_lag_list)

# join lagged variables back to original data
vacantparcel_crime <- left_join(vacantparcel_crime, parcel_lag %>% as.data.frame() %>% select(miyvpc_parcel_id, year, contains("summerdensity_lag")), by = c("miyvpc_parcel_id", "year"))
```

# description of the data

```{r}
table1(~year_cat + pop_dens + disadvantage_index + p1crime_summerdensity_sqmile + p1violcrime_summerdensity_sqmile + p1youthviolcrime_summerdensity_sqmile + p1violguncrime_summerdensity_sqmile + p1youthviolguncrime_summerdensity_sqmile | ownmain, data = vacantparcel_crime)
```

# run gclb ownership analyses, based only on GCLB/vacant properties

```{r}
# TEST MODELS TO ILLUSTRATE AUTOCORRELATION ISSUES
# associations between GCLB ownership and all crime

# lmer non-spatial model
lmer_gclbvac_all_ns <- lmer(
  p1crime_summerdensity_sqmile ~
    gclb_property*year0 +
    disadvantage_index +
    pop_dens +
    (1|miyvpc_parcel_id),
  data = vacantparcel_crime
)

summary(lmer_gclbvac_all_ns)

# lmer spatial lag model
lmer_gclbvac_all <- lmer(
  p1crime_summerdensity_sqmile ~
    gclb_property*year0 +
    disadvantage_index +
    pop_dens +
    p1crime_summerdensity_lag +
    (1|miyvpc_parcel_id),
  data = vacantparcel_crime
)

summary(lmer_gclbvac_all)

# trend surface gam model
gam_gclbvac_all <- gamm4(
  p1crime_summerdensity_sqmile ~ 
    gclb_property*year0 + 
    disadvantage_index +
    pop_dens +
    s(X, Y),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime
)

summary(gam_gclbvac_all$gam)
vis.gam(gam_gclbvac_all$gam, view = c("X", "Y"), plot.type = "persp", theta = 45, phi = 45)

# trend surface gam model, increased knots
gam_gclbvac_all <- gamm4(
  p1crime_summerdensity_sqmile ~ 
    gclb_property*year0 + 
    disadvantage_index +
    pop_dens +
    s(X, Y, k = 50, fx = TRUE),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime
)

summary(gam_gclbvac_all$gam)
vis.gam(gam_gclbvac_all$gam, view = c("X", "Y"), plot.type = "persp", theta = 45, phi = 45)

# trend surface gam model, increased knots, maximum likelihood
gam_gclbvac_all_ml <- gamm4(
  p1crime_summerdensity_sqmile ~ 
    gclb_property*year0 + 
    disadvantage_index +
    pop_dens +
    s(X, Y, k = 50, fx = TRUE),
  random = ~(1|miyvpc_parcel_id),
  REML = FALSE,
  data = vacantparcel_crime
)

summary(gam_gclbvac_all_ml$gam)
vis.gam(gam_gclbvac_all$gam, view = c("X", "Y"), plot.type = "persp", theta = 45, phi = 45)

# trend surface gam model, increased knots, with lag
gamlag_gclbvac_all <- gamm4(
  p1crime_summerdensity_sqmile ~ 
    gclb_property*year0 + 
    disadvantage_index +
    pop_dens +
    p1crime_summerdensity_lag +
    s(X, Y, k = 50, fx = TRUE),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime
)

summary(gamlag_gclbvac_all$gam)
vis.gam(gamlag_gclbvac_all$gam, view = c("X", "Y"), plot.type = "persp", theta = 45, phi = 45)
```

```{r}
# associations between GCLB ownership and all crime
gam_gclbvac_all <- gamm4(
  p1crime_summerdensity_sqmile ~ 
    gclb_property*year0 + 
    disadvantage_index +
    pop_dens +
    s(X, Y, k = 50),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime
)

summary(gam_gclbvac_all$gam)

# associations between GCLB ownership and violent crime
gam_gclbvac_viol <- gamm4(
  p1violcrime_summerdensity_sqmile ~ 
    gclb_property*year0 + 
    pop_dens + 
    disadvantage_index +
    s(X, Y, k = 50),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime
)

summary(gam_gclbvac_viol$gam)

# associations between GCLB ownership and youth-involved violent crime
gam_gclbvac_youthviol <- gamm4(
  p1youthviolcrime_summerdensity_sqmile ~ 
    gclb_property*year0 + 
    pop_dens + 
    disadvantage_index +
    s(X, Y, k = 50),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime
)

summary(gam_gclbvac_youthviol$gam)

# associations between GCLB ownership and gun crime
gam_gclbvac_gun <- gamm4(
  p1violguncrime_summerdensity_sqmile ~ 
    gclb_property*year0 + 
    pop_dens + 
    disadvantage_index +
    s(X, Y, k = 50),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime
)

summary(gam_gclbvac_gun$gam)

# associations between GCLB ownership and youth-involved gun crime
gam_gclbvac_youthgun <- gamm4(
  p1youthviolguncrime_summerdensity_sqmile ~ 
    gclb_property*year0 + 
    pop_dens + 
    disadvantage_index +
    s(X, Y, k = 50),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime
)

summary(gam_gclbvac_youthgun$gam)
```

```{r}
# table results
model <- gam_gclbvac_youthgun$gam

summary(model)

cbind(estimate = coefficients(model), confint(model)) %>% round(digits = 4) %>% as.data.frame() %>% transmute(vars = row.names(.), report = str_c(estimate, " (", `2.5 %`, ", ", `97.5 %`, ")")) %>% filter(grepl("s\\(X,Y\\)", vars) == F)
```

# run ownership/maintenance analyses

```{r}
# associations between GCLB ownership and all crime
gam_mowvac_all <- gamm4(
  p1crime_summerdensity_sqmile ~ 
    ownmain*year0 + 
    disadvantage_index +
    pop_dens +
    s(X, Y, k = 50),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime
)

summary(gam_mowvac_all$gam)

# associations between GCLB ownership and violent crime
gam_mowvac_viol <- gamm4(
  p1violcrime_summerdensity_sqmile ~ 
    ownmain*year0 + 
    pop_dens + 
    disadvantage_index +
    s(X, Y, k = 50),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime
)

summary(gam_mowvac_viol$gam)

# associations between GCLB ownership and youth-involved violent crime
gam_mowvac_youthviol <- gamm4(
  p1youthviolcrime_summerdensity_sqmile ~ 
    ownmain*year0 + 
    pop_dens + 
    disadvantage_index +
    s(X, Y, k = 50),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime
)

summary(gam_mowvac_youthviol$gam)

# associations between GCLB ownership and gun crime
gam_mowvac_gun <- gamm4(
  p1violguncrime_summerdensity_sqmile ~ 
    ownmain*year0 + 
    pop_dens + 
    disadvantage_index +
    s(X, Y, k = 50),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime
)

summary(gam_mowvac_gun$gam)

# associations between GCLB ownership and youth-involved gun crime
gam_mowvac_youthgun <- gamm4(
  p1youthviolguncrime_summerdensity_sqmile ~ 
    ownmain*year0 + 
    pop_dens + 
    disadvantage_index +
    s(X, Y, k = 50),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime
)

summary(gam_mowvac_youthgun$gam)

```

```{r}
# table results
model <- gam_mowvac_youthgun$gam

summary(model)

cbind(estimate = coefficients(model), confint(model)) %>% round(digits = 4) %>% as.data.frame() %>% transmute(vars = row.names(.), report = str_c(estimate, " (", `2.5 %`, ", ", `97.5 %`, ")")) %>% filter(grepl("s\\(X,Y\\)", vars) == F)
```

# CnG group analyses

```{r}
# associations between GCLB ownership and all crime
gam_cngareavac_all <- gamm4(
  p1crime_summerdensity_sqmile ~ 
    cng_area*year0 + 
    disadvantage_index +
    pop_dens +
    s(X, Y, k = 50),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime %>% filter(any_maintenance == FALSE)
)

summary(gam_cngareavac_all$gam)

# associations between GCLB ownership and violent crime
gam_cngareavac_viol <- gamm4(
  p1violcrime_summerdensity_sqmile ~ 
    cng_area*year0 + 
    pop_dens + 
    disadvantage_index +
    s(X, Y, k = 50),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime %>% filter(any_maintenance == FALSE)
)

summary(gam_cngareavac_viol$gam)

# associations between GCLB ownership and youth-involved violent crime
gam_cngareavac_youthviol <- gamm4(
  p1youthviolcrime_summerdensity_sqmile ~ 
    cng_area*year0 + 
    pop_dens + 
    disadvantage_index +
    s(X, Y, k = 50),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime %>% filter(any_maintenance == FALSE)
)

summary(gam_cngareavac_youthviol$gam)

# associations between GCLB ownership and gun crime
gam_cngareavac_gun <- gamm4(
  p1violguncrime_summerdensity_sqmile ~ 
    cng_area*year0 + 
    pop_dens + 
    disadvantage_index +
    s(X, Y, k = 50),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime %>% filter(any_maintenance == FALSE)
)

summary(gam_cngareavac_gun$gam)

# associations between GCLB ownership and youth-involved gun crime
gam_cngareavac_youthgun <- gamm4(
  p1youthviolguncrime_summerdensity_sqmile ~ 
    cng_area*year0 + 
    pop_dens + 
    disadvantage_index +
    s(X, Y, k = 50),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime %>% filter(any_maintenance == FALSE)
)

summary(gam_cngareavac_youthgun$gam)

```

# Distance to nearest maintained parcel

```{r}
vacantparcel_crime <- vacantparcel_crime %>% 
  group_by(miyvpc_parcel_id) %>% 
  arrange(year) %>% 
  mutate(
    dist_to_maintained = as.numeric(dist_to_maintained),
    p1crime_sd_sqm_yearlag = lag(p1crime_summerdensity_sqmile),
    p1crime_yoy_chg = ((p1crime_summerdensity_sqmile - p1crime_sd_sqm_yearlag) / p1crime_sd_sqm_yearlag) * 100,
    dist_cat = case_when(
      dist_to_maintained > 0 & dist_to_maintained <= 50 ~ "A. 0-50",
      dist_to_maintained > 50 & dist_to_maintained <= 100 ~ "B. 50-100",
      dist_to_maintained > 100 & dist_to_maintained <= 150 ~ "C. 100-150",
      dist_to_maintained > 150 & dist_to_maintained <= 200 ~ "D. 150-200",
      dist_to_maintained > 200 & dist_to_maintained <= 250 ~ "E. 200-250",
      dist_to_maintained > 250 & dist_to_maintained <= 300 ~ "F. 250-300",
      dist_to_maintained > 300 & dist_to_maintained <= 350 ~ "G. 300-350",
      dist_to_maintained > 350 & dist_to_maintained <= 400 ~ "H. 350-400",
      dist_to_maintained > 400 & dist_to_maintained <= 450 ~ "I. 400-450",
      dist_to_maintained > 450 & dist_to_maintained <= 500 ~ "J. 450-500",
      TRUE ~ "K. 500+"
    ),
    dist_cat = factor(dist_cat, levels = c("A. 0-50", "B. 50-100", "C. 100-150", "D. 150-200", "E. 200-250", "F. 250-300", "G. 300-350", "H. 350-400", "I. 400-450", "J. 450-500", "K. 500+"))
  ) %>% 
  ungroup() %>% 
  arrange(miyvpc_parcel_id)

# associations between GCLB ownership and all crime
gam_distan_all <- gamm4(
  p1crime_summerdensity_sqmile ~ 
    dist_cat*year0 +
    disadvantage_index +
    pop_dens +
    s(X, Y),
  random = ~(1|miyvpc_parcel_id),
  data = vacantparcel_crime %>% filter(any_maintenance == FALSE)
)

summary(gam_distan_all$gam)

# plot
vacantparcel_crime %>%
  ggplot(aes(x = year, y = p1crime_summerdensity_sqmile, color = dist_cat)) +
  geom_smooth(method = "loess", se = FALSE) +
  theme_classic() +
  labs(x = "Year", y = "P1 Crime Density", color = "Dist. to Nearest/nMaintained Parcel")
```

# Moran's I test for models

```{r}
set.seed(20210811)

# specify which model you want to calculate Moran's I for
# (call it mi_model, so the code below doesn't need to be changed)
mi_model <- gam_gclbvac_all$gam

# bind residuals to model frame
mi_residframe <- cbind(model.frame(mi_model), residuals = residuals(mi_model))

# merge spatial information onto residframe from zip_coords object
# calculate total residual for each unit/location
mi_residframe <- mi_residframe %>%
  #left_join(., vacantparcel_crime %>% select(miyvpc_parcel_id, X, Y), by = c("miyvpc_parcel_id")) %>%
  filter(year0 == 1) %>%
  group_by(miyvpc_parcel_id) %>%
  summarise(residuals = first(residuals), X = first(X), Y = first(Y)) %>%
  ungroup() %>%
  distinct() %>%
  st_as_sf(coords = c("X", "Y"), crs = 6498)

mi_residframe_coords <- coordinates(as(mi_residframe, "Spatial"))

# map residuals
ggplot(mi_residframe) + geom_sf(aes(color = residuals), alpha = 0.6) + theme_classic()

# calculate the inverse distance weights matrix (neighbors are street segments within 1000 meters)
resid_neighbors <- dnearneigh(mi_residframe_coords, 0, 300)
# resid_neigh_dists <- nbdists(resid_neighbors, mi_residframe_coords)
# resid_idw <- lapply(resid_neigh_dists, function(x) (1/(x)))
resid_idw_weights <- nb2listw(resid_neighbors, zero.policy = TRUE)

# use same weights matrix as we used to calculate lagged variable
moran.test(mi_residframe$residuals, resid_idw_weights, zero.policy = TRUE)
```

# Parked Code

```{r}
# inverse distance weights matrix for points (inverse distance is one of many methods)
site_dists <- as.matrix(dist(cbind(mi_residframe$X, mi_residframe$Y)))
site_dists_inv <- 1/site_dists
site_dists_inv[is.infinite(site_dists_inv)] <- 0   

# calculate Moran's I statistic using ape package
Moran.I(mi_residframe$residuals, site_dists_inv)

# # check autocorrelation continuously
mi_residframe <- mi_residframe %>%
  mutate(
    X = st_coordinates(.)[,"X"],
    Y = st_coordinates(.)[,"Y"]
  )
# 
mi_residuals_saplot <- spline.correlog(x=mi_residframe$X, y=mi_residframe$Y, z=mi_residframe$residuals, resamp=100, quiet=TRUE)
plot(mi_residuals_saplot)
```